The \dealii{} Library, Version 8.5

### 2017-03-03 8.5/paper.tex
add myself to the authors

\hypersetup{
  pdfauthor={
    Wolfgang Bangerth,
    Timo Heister
  },
  pdftitle={The deal.II Library, Version 8.5, 2017},
}

@@

\author[2]{Timo Heister}
\affil[2]{Mathematical Sciences,
  O-110 Martin Hall,
  Clemson University,
  Clemson, SC 29634, USA.
  {\texttt{heister@clemson.edu}}}

>>>>

\hypersetup{
  pdfauthor={
    Wolfgang Bangerth,
    Denis Davydov
    Timo Heister
  },
  pdftitle={The deal.II Library, Version 8.5, 2017},
}

@@

\author[2]{Denis Davydov}
\affil[2]{Chair of Applied Mechanics, University of
     Erlangen-Nuremberg, Egerlandstr.\ 5, 91058 Erlangen, Germany.
    {\texttt{denis.davydov@fau.de}}}

\author[3]{Timo Heister}
\affil[3]{Mathematical Sciences,
  O-110 Martin Hall,
  Clemson University,
  Clemson, SC 29634, USA.
  {\texttt{heister@clemson.edu}}}
